---
title: "gimme-multiverse"
author: "Björn Siepe"
date: "`r Sys.Date()`"
output: html_document
---

In this document, we perform multiverse analysis for two datasets.


# Preparation
Load all relevant packages:
```{r packages}
library(mvgimme)       # fork of gimmme package that allows multiverse
library(tidyverse)     # data handling
library(here)          # reproducible folder settings
library(tictoc)
source("aux_funs.R")
set.seed(35037)
```


# Load reference fits
We load the reference fits, i.e. results of GIMME as reported in the literature. 

```{r load-ref-fits}
ref_fit_pers <- readRDS(here("data/wright_2019/wright_2019_fit_nondetrend.RDS"))
ref_fit_emot <- readRDS(here("data/kullar_2023/kullar_2023_fit.RDS"))
```



# Fit multiverse

Multiverse parameters:
```{r multiverse-params}

group_cuts <- c(.50, .60, .75, .80)
sub_cuts <- c(.50, .60, .75, .80)
rmsea_cuts <- c(.03, .05, .08)
srmr_cuts <- c(.03, .05, .08)
nnfi_cuts <- c(.90, .95, .97)
cfi_cuts <- c(.90, .95, .97)
n_excels <- c(1, 2, 3)

multiverse_grid <- expand.grid(
  group_cuts = group_cuts,
  sub_cuts = sub_cuts,
  rmsea_cuts = rmsea_cuts,
  srmr_cuts = srmr_cuts,
  nnfi_cuts = nnfi_cuts,
  cfi_cuts = cfi_cuts,
  n_excels = n_excels
)

```




## Personality Dataset
```{r multiverse-personality}
# for testing
data_list <- readRDS(here("data/wright_2019/data_list.RDS"))
tic()
mv_res_pers <- mvgimme::multiverse.gimme(data = here("data/wright_2019/individual_files"),
                                         sep = ",",
                                         header = TRUE,
                          groupcutoffs = group_cuts, 
                          subcutoffs = sub_cuts,
                          rmsea.cuts = rmsea_cuts,
                          srmr.cuts = srmr_cuts,
                          nnfi.cuts = nnfi_cuts,
                          cfi.cuts = cfi_cuts,
                          n.excellent = n_excels,
                          n.cores = 60,
                          prune_output = TRUE,
                          save_output = TRUE)
toc()

# even more testing





mv_res_pers <- mvgimme::multiverse.gimme(data = "data/wright_2019/individual_files",
                          groupcutoffs = c(.50, .60, .75, .80), 
                          subcutoffs = c(.50, .60, .75, .80),
                          rmsea.cuts = c(.03, .05, .08),
                          srmr.cuts = c(.03, .05, .08),
                          nnfi.cuts = c(.90, .95, .97),
                          cfi.cuts = c(.90, .95, .97),
                          n.excellent = c(1, 2, 3),
                          n.cores = 60,
                          prune_output = TRUE,
                          save_output = TRUE, 
                          save_dir = "output/mv_personality")
saveRDS(mv_res_pers, file = here("output/mv_personality/mv_res_pers.RDS"))

```



## Emotion Dataset

```{r multiverse-personality}
mv_res_emot <- mvgimme::multiverse.gimme(data = "data/kullar_2023/finaloutput",
                          groupcutoffs = c(.50, .60, .75, .80), 
                          subcutoffs = c(.50, .60, .75, .80),
                          rmsea.cuts = c(.03, .05, .08),
                          srmr.cuts = c(.03, .05, .08),
                          nnfi.cuts = c(.90, .95, .97),
                          cfi.cuts = c(.90, .95, .97),
                          n.excellent = c(1, 2, 3),
                          n.cores = 1,
                          prune_output = TRUE,
                          save_output = TRUE, 
                          save_dir = "output/mv_emotion")
```


# Analyze multiverse

## Personality Dataset
Delete reference fit from multiverse dataset:
```{r}
mv_res_pers <- subset(mv_res_pers, !(group_cuts == .75 &
                        sub_cuts == .75 &
                        rsmea_cuts == .05 &
                        srms_cuts == .05 &
                        nnfi_cuts == .95 &
                        cfi_cuts == .95 &
                        n_excels == 2))
```





## Emotion Dataset
Delete reference fit from multiverse dataset:
```{r}
mv_res_emot <- subset(mv_res_emot, !(group_cuts == .75 &
                        sub_cuts == .75 &
                        rsmea_cuts == .05 &
                        srms_cuts == .05 &
                        nnfi_cuts == .95 &
                        cfi_cuts == .95 &
                        n_excels == 2))


```



# Visualize Multiverse

## Personality Dataset

### Manuscript


### Supplement


## Emotion Dataset

### Manuscript


### Supplement