---
title: "GIMME Cutoff Simulation"
author: "Björn Siepe"
date: "`r Sys.Date()`"
output: html_document
---

This document contains code for a small simulation on using different fit index cutoffs
as stopping criteria for GIMME. 

# Preparation
```{r packages}
library(mvgimme)    # multiverse gimme
library(SimDesign)  # simulation design
library(here)
source(here::here("scripts/aux_funs.R"))

```

Reproducibility
```{r reproducibility}
set.seed(35037)
```





# Simulation settings
Create a design with different sample sizes and time series lengths.
Maybe also different sparsity levels? 
```{r sim-settings}
# sample_sizes <- c(50, 100, 200)
# For testing only:
sample_sizes <- c(30, 80)
# sample_sizes <- c(30)
ar <- c(.2)
ind_a <- c(.15, .40)
# ind_a <- c(.15)
ind_phi <- c(.05, .25)
replications <- 500

sim_design <- SimDesign::createDesign(sample_size = sample_sizes,
                                      ar = ar,
                                      ind_a = ind_a,
                                      ind_phi = ind_phi)


# TODO double check if this works with change_phi and change_a
a_1 <- matrix(c(
  0.00, 0.00, 0.00, 0.00, 0.00, 0.00,
  0.00, 0.00, 0.25, 0.40, 0.00, 0.00,
  0.00, 0.00, 0.00, 0.00, 0.00, 0.00,
  0.00, 0.00, 0.00, 0.00, 0.00, 0.00,
  0.00, 0.00, 0.00, 0.00, 0.00, 0.15,
  0.00, 0.00, 0.35, 0.00, 0.00, 0.00
), nrow = 6, byrow = TRUE)

change_a <- matrix(c(
  0, 0,  0.00000000,  0.00000000, 0,  0.00000000,
  0, 0, -0.01010176, -0.06727818, 0,  0.00000000,
  0, 0,  0.00000000,  0.00000000, 0,  0.00000000,
  0, 0,  0.00000000,  0.00000000, 0,  0.00000000,
  0, 0,  0.20420106,  0.00000000, 0, -0.04994893,
  0, 0, -0.35000000,  0.00000000, 0,  0.00000000
), nrow = 6, byrow = TRUE)

phi_1 <- matrix(c(
  ar, 0.00, 0.00, 0.00, 0.00, 0.00,
  0.00, ar, 0.00, 0.00, 0.10, 0.00,
  0.00, 0.00, ar, 0.00, 0.00, 0.20,
  0.00, 0.00, 0.00, ar, 0.00, 0.00,
  0.00, 0.00, 0.00, 0.00, ar, 0.00,
  0.00, 0.00, 0.00, 0.00, 0.00, ar
), nrow = 6, byrow = TRUE)
change_phi <- matrix(c(
  0.0299806, 0.0000000, 0.0000000,  0.00000000,  0.0000000,  0.00000000,
  0.0000000, 0.1384933, 0.0000000,  0.00000000,  0.2270527,  0.00000000,
  0.0000000, 0.0000000, 0.2266066,  0.00000000,  0.0000000, -0.02793758,
  0.0000000, 0.0000000, 0.0000000, -0.06865572,  0.0000000,  0.00000000,
  0.0000000, 0.0000000, 0.0000000,  0.00000000, -0.1298429,  0.00000000,
  0.0000000, 0.0000000, 0.0000000,  0.00000000,  0.0000000,  0.05377093
), nrow = 6, byrow = TRUE)
phi_2 <- phi_1 + change_phi
phi_list <- list(phi_1, phi_2)

psi_mat <- matrix(data = rep(0, 36), nrow = 6, ncol = 6)
diag(psi_mat) <- rep(1, 6)
psi_list <- list(psi_mat, psi_mat)


sim_pars <- list(
  t = 100,
  phi_list = phi_list,
  a_1 = a_1,
  psi_list = psi_list,
  change_a = change_a
)

```



# Data Generation

Then, create data-generation function to sample from this model, using `gimme`.
```{r data-generation}
sim_generate <- function(condition, 
                         fixed_objects = NULL){
  # obtain fixed parameters
  SimDesign::Attach(fixed_objects)
  
  # obtain condition parameters
  n <- condition$sample_size
  group_ind <- c(rep(1, (n/2)), rep(2, (n/2)))
  ar <- condition$ar
  ind_a <- condition$ind_a
  ind_phi <- condition$ind_phi
  
  # Create matrix list depending on AR effect
  diag(a_1) <- rep(ar, 6)
  a_2 <- a_1 + change_a
  a_list <- list(a_1, a_2)
  tries <- 0
  max_tries <- 100
  while (tries < max_tries) {
    sim_dat <- try(simulateVARtest(
                                   A = a_list, 
                                   Phi = phi_list,
                                   Psi = psi_list,
                                   subAssign = group_ind,
                                   N = n,
                                   Obs = t,
                                   indA = ind_a,
                                   indPhi = ind_phi))
     if (!inherits(sim_dat, "try-error")) {
        break
    } else {
        if (tries == max_tries) {
            break
        }
    
    }
  }
  
  # save dgp
  saveRDS(sim_dat, file = paste0(here("output/simulation/sim_dat_"), n, "_", t,
                                   ".RDS"))
  
  # list of data matrices
  l_dat <- lapply(sim_dat$dataList, function(x){
    as.matrix(x, ncol = nvar)
  })
  
  # list of edge weights
  l_paths <- lapply(sim_dat$indList, function(x){
    x$Paths
  })
  
  # overall counts matrix
  l_counts <- lapply(sim_dat$indList, function(x){
    x$Adj
  })
  path_counts <- Reduce('+', l_counts)
  
  
  dat <- list(dat = l_dat, 
              ind_paths = l_paths, 
              path_counts = path_counts, 
              group_ind = group_ind)
  # levels = sim_dat$levels))
  
  return(dat)
}


# sim_generate_old <- function(condition, 
#                          fixed_objects = NULL){
#   # obtain fixed parameters
#   SimDesign::Attach(fixed_objects)
#   
#   # obtain condition parameters
#   n <- condition$sample_size
#   t <- condition$ts_length
#   d <- condition$densities
#   
#     sim_dat <- try(sim.gimme(
#                    p.con = p.con, 
#                    nvar = nvar,
#                    AR = AR,
#                    dens = d,
#                    p.group = p.group,
#                    con.b = con.b,
#                    lag.b = lag.b,
#                    mat = mat, 
#                    lvl = lvl,          
#                    t = t,              
#                    n.ind = n))
#  
#   
#   # save dgp
#   saveRDS(sim_dat, file = paste0("output/sim_dat_", n, "_", t,
#                                    ".RDS"))
#   
#   # list of data matrices
#   l_dat <- lapply(sim_dat, function(x){
#     as.matrix(x$series, ncol = nvar)
#   })
#   
#   # list of edge weights
#   l_paths <- lapply(sim_dat, function(x){
#     x$paths
#   })
#   
#   # overall counts matrix
#   l_counts <- lapply(sim_dat, function(x){
#     ifelse(x$paths != 0, 1, 0)
#   })
#   path_counts <- Reduce('+', l_counts)
#   
#   
#   dat <- list(dat = l_dat, ind_paths = l_paths, path_counts = path_counts)
#   # levels = sim_dat$levels))
# }

```




# Fitting functions
We use standard GIMME, and 3 different threshold methods in mvgimme. 
```{r fitting-methods}
sim_analyse_gimme_default <- function(condition, dat, fixed_objects = NULL){
  
  # obtain fixed objects
  Attach(fixed_objects)
  
  # save dgp parameters for later
  dgp_ind_paths <- dat$ind_paths
  dgp_path_counts <- dat$path_counts
  dgp_sub_ind <- dat$group_ind
  
  gimme_res <- try(multiverse.gimme(data = dat$dat,
                 ar = TRUE, 
                 subgroup = TRUE,
                 groupcutoff = .75,
                 subcutoff   = .75))
 
  
  ret <- list(path_counts = gimme_res[[1]]$path_counts,
              path_est_mats = gimme_res[[1]]$path_est_mats,
              sub_ind = gimme_res[[1]]$fit$sub_membership,
              dgp_path_counts = dgp_path_counts,
              dgp_ind_paths = dgp_ind_paths,
              dgp_sub_ind = dgp_sub_ind)
  ret
}

sim_analyse_gimme_liberal <- function(condition, dat, fixed_objects = NULL){
  
  # obtain fixed objects
  Attach(fixed_objects)
  
  # save dgp parameters for later
  dgp_ind_paths <- dat$ind_paths
  dgp_path_counts <- dat$path_counts
  dgp_sub_ind <- dat$group_ind
  
  gimme_res <- try(multiverse.gimme(data = dat$dat,
                 ar = TRUE, 
                 subgroup = TRUE,
                 groupcutoff = .75,
                 subcutoff   = .75,
                 rmsea.cuts = .08,
                 srmr.cuts = .08,
                 nnfi.cuts = .90,
                 cfi.cuts = .90))
  
    ret <- list(path_counts = gimme_res[[1]]$path_counts,
              path_est_mats = gimme_res[[1]]$path_est_mats,
              sub_ind = gimme_res[[1]]$fit$sub_membership,
              dgp_path_counts = dgp_path_counts,
              dgp_ind_paths = dgp_ind_paths,
              dgp_sub_ind = dgp_sub_ind)
  ret
  
}

sim_analyse_gimme_strict <- function(condition, dat, fixed_objects = NULL){
  
  # obtain fixed objects
  Attach(fixed_objects)
  
  # save dgp parameters for later
  dgp_ind_paths <- dat$ind_paths
  dgp_path_counts <- dat$path_counts
  dgp_sub_ind <- dat$group_ind
  
  gimme_res <- try(multiverse.gimme(data = dat$dat,
                 ar = TRUE, 
                 subgroup = TRUE,
                 groupcutoff = .75,
                 subcutoff   = .75,
                 rmsea.cuts = .03,
                 srmr.cuts = .03,
                 nnfi.cuts = .97,
                 cfi.cuts = .97
                 ))
  ret <- list(path_counts = gimme_res[[1]]$path_counts,
              path_est_mats = gimme_res[[1]]$path_est_mats,
              sub_ind = gimme_res[[1]]$fit$sub_membership,
              dgp_path_counts = dgp_path_counts,
              dgp_ind_paths = dgp_ind_paths,
              dgp_sub_ind = dgp_sub_ind)
  ret
  
}

sim_analyse_gimme_threshold1 <- function(condition, dat, fixed_objects = NULL){
  
  # obtain fixed objects
  Attach(fixed_objects)
  
  # save dgp parameters for later
  dgp_ind_paths <- dat$ind_paths
  dgp_path_counts <- dat$path_counts
  dgp_sub_ind <- dat$group_ind
  
  gimme_res <- try(multiverse.gimme(data = dat$dat,
                 ar = TRUE, 
                 subgroup = TRUE,
                 groupcutoff = .75,
                 subcutoff   = .75,
                 n.excellent = 1))
  
  ret <- list(path_counts = gimme_res[[1]]$path_counts,
              path_est_mats = gimme_res[[1]]$path_est_mats,
              sub_ind = gimme_res[[1]]$fit$sub_membership,
              dgp_path_counts = dgp_path_counts,
              dgp_ind_paths = dgp_ind_paths,
              dgp_sub_ind = dgp_sub_ind)
  ret
  
  
}



```



# Summary function


Helpers:
```{r}
#--- Compute Precision
precision <- function(true, est){
  # true paths relative to all paths
  true_pos <- sum(true & est)
  all_pos <- sum(est)
  
  if (all_pos == 0) {
    return(0)
  } else {
    precision <- true_pos / all_pos
    return(precision)
  }
}

#--- Compute Recall
recall <- function(true, est) {
  true_pos <- sum(true & est)
  all_true <- sum(true)
  
  if (all_true == 0) {
    return(0)
  } else {
    recall <- true_pos / all_true
    return(recall)
  }
}




#--- Nondirected Adjacency matrix
nondirect_adjacency <- function(adj_mat) {
  # Number of ariables
  n_adj_vars <- nrow(adj_mat)
  
  # Initialize symmetrical matrix with 0s
  sym_matrix <- matrix(0, nrow = n_adj_vars, ncol = n_adj_vars)
  
  # Iterate through each cell of the original matrix
  for (i in 1:n_adj_vars) {
    for (j in 1:n_adj_vars) {
      # If there is any effect (1) in either direction, update the symmetrical matrix
      if (n_adj_vars[i, j] == 1 || n_adj_vars[j, i] == 1) {
        sym_matrix[i, j] <- 1
        sym_matrix[j, i] <- 1
      }
    }
  }

  return(sym_matrix)
}


abs_mean <- function(x){
  mean(abs(x))
}
abs_med <- function(x){
  stats::median(abs(x))
}

abs_sum <- function(x){
  sum(abs(x))
}
```




This is relevant here: http://philchalmers.github.io/SimDesign/html/04-Auxillary_parameter_recovery.html

```{r summary-function}
sim_summarize <- function(condition, results, fixed_objects = NULL){

  
  ret <- list()
  #---- Loop over different analysis fns -----
  for(m in 1:length(results[[1]])){
    
  
  
  #----- Subgroup ------
  ari_sub <- lapply(seq_along(results), function(i){
    
    if(is.null(results[[i]][[m]]$sub_ind)){
      NULL
    } 
    else{
      perturbR:::arandi(results[[i]][[m]]$dgp_sub_ind, results[[i]][[m]]$sub_ind)
    }
    
  })
  
  
  
  #----- Individual -----
  
  # Compare overall path counts
  diff_path_counts <- lapply(seq_along(results), function(i){
    sum(results[[i]][[m]]$dgp_path_counts - results[[i]][[m]]$path_counts)
  })
  
  # Compute bias
  bias_paths <- lapply(seq_along(results), function(i){
     l_diff <- Map('-', results[[i]][[m]]$dgp_ind_paths, results[[i]][[m]]$path_est_mats)
     lapply(l_diff, function(y){as.matrix(y)})
  })
  
  # Precision
  precision_directed <- lapply(seq_along(results), function(i){
    precision(results[[i]][[m]]$dgp_path_counts, results[[i]][[m]]$path_counts)
  })
  
  # Recall
  recall_directed <- lapply(seq_along(results), function(i){
    recall(results[[i]][[m]]$dgp_path_counts, results[[i]][[m]]$path_counts)
  })
  
  
  #----- Aggregate -----
  diff_path_counts_mean <- mean(unlist(diff_path_counts))
  diff_path_counts_sd <- sd(unlist(diff_path_counts))
  
  # Aggregate ARI
  ari_mean <- mean(unlist(ari_sub))
  ari_sd <- sd(unlist(ari_sub))
  
  
  # Recall and Precision
  precision_directed_mean <- mean(unlist(precision_directed))
  precision_directed_mcse <- sqrt((precision_directed_mean*(1-precision_directed_mean)) / replications)
  recall_directed_mean <- mean(unlist(precision_directed))
  recall_directed_mcse <- sqrt((recall_directed_mean*(1-recall_directed_mean)) / replications)
  
  
  # Aggregate bias
  mean_bias_ests <- lapply(bias_paths, function(x){
    l_tmp <- list()
    mean_mat <- apply(simplify2array(x), 1:2, mean)
    l_tmp$mean_nonzero_diff <- mean(abs(mean_mat[mean_mat != 0]))
    l_tmp$var_nonzero_diff <- var(abs(mean_mat[mean_mat != 0]))
    l_tmp$mean_diff <- mean(abs(mean_mat))
    l_tmp$var_diff <- var(abs(mean_mat))
    return(l_tmp)
  })
  
  # for MCSE formulas, see Morris et al. 2019 SIM
  bias_nonzero_mean <- abs_mean(sapply(mean_bias_ests, function(x) x$mean_nonzero_diff))
  bias_nonzero_mcse <- sqrt(sum(sapply(mean_bias_ests, function(x) x$var_nonzero_diff)) / (replications * (replications - 1)))
  bias_mean <- abs_mean(sapply(mean_bias_ests, function(x) x$mean_diff))
  bias_mcse <- sqrt(sum(sapply(mean_bias_ests, function(x) x$var_diff)) / (replications * (replications - 1)))
  
  
  # Output
  ret_mod <- c(ari_mean = ari_mean,
           ari_sd = ari_sd,
           precision_directed_mean = precision_directed_mean,
           recall_directed_mean = recall_directed_mean,
           diff_path_counts_mean = diff_path_counts_mean,
           bias_nonzero_mean = bias_nonzero_mean,
           bias_nonzero_mcse = bias_nonzero_mcse,
           bias_mean = bias_mean,
           bias_mcse = bias_mcse
           )
  ret_mod <- unlist(ret_mod)
  ret[[m]] <- ret_mod
  
  names(ret)[m] <- names(results[[1]])[m]
  # Add model name
  # names(ret[[m]]) <- paste0(names(ret[[m]]), names(results[[1]])[m])
  
  }
  

  ret <- unlist(ret)
  # ret <- unname(ret)
  return(ret)
}
```




# Execute Simulation

```{r}

sim_res <- SimDesign::runSimulation(sim_design, 
                                    replications = replications, 
                                    save_results = TRUE,
                                    generate = sim_generate, 
                                    analyse = list(
                                    gimme = sim_analyse_gimme_default, 
                                    liberal = sim_analyse_gimme_liberal, 
                                    strict = sim_analyse_gimme_strict,
                                    thresh = sim_analyse_gimme_threshold1
                                    ),
                                    # analyse = sim_analyse_gimme_liberal,
                                    summarise = sim_summarize, 
                                    # save = TRUE, 
                                    # save_seeds = TRUE,
                                    packages = c("mvgimme", "here"), 
                                    fixed_objects = sim_pars,
                                    parallel = TRUE)
SimClean()

# maybe try unname() on the aux_funs results
```


# Keeping Track of common bugs:
Error in do.call(data.frame, c(x, alis)) : 
  variable names are limited to 10000 bytes - ?????


