---
title: "GIMME Cutoff Simulation"
author: "Björn Siepe"
date: "`r Sys.Date()`"
output: html_document
---

This document contains code for a small simulation on using different fit index cutoffs
as stopping criteria for GIMME. 

# Preparation
```{r packages}
library(mvgimme)    # multiverse gimme
library(SimDesign)  # simulation design
library(here)
source(here::here("scripts/aux_funs.R"))

```

Reproducibility
```{r reproducibility}
set.seed(35037)
```





# Simulation settings
Create a design with different sample sizes and time series lengths.
Maybe also different sparsity levels?
```{r sim-settings}
# sample_sizes <- c(50, 100, 200)
# For testing only:
sample_sizes <- c(20)
# ts_lengths <- c(50, 100, 200)
ts_lengths <- c(50,100)
replications <- 1000

sim_design <- SimDesign::createDesign(sample_size = sample_sizes,
                                  ts_length = ts_lengths)

sim_pars <- list(
  p.con = .50, 
  nvar = 6, 
  AR =.3,
  p.group = .50,
  dens = .20,
  con.b = .6,
  lag.b = -.3
)

```



# Data Generation
```{r true-dgp}
# test_mat <- mat.generate.asw(p.con = .50, 
#                  nvar = 6, AR=.3,
#                  p.group = .50,dens = .20,
#                  con.b = .6,lag.b = -.3)
# out <- ts.generate.asw(mat = test_mat$sub1,
#                              lvl = test_mat$lvl1,
#                              t   = 100,
#                              p.group = .50,dens = .20,
#                              con.b = .6,lag.b = -.3,
#                              p.con = .50)
# 
# res <- sim.gimme(p.con = .50, 
#                  nvar = 6, AR=.3,
#                  p.group = .50,dens = .20,
#                  con.b = .6,lag.b = -.3,
#                  n.ind = 20, t = 100)
# 


```

Use functions from here: 
https://github.com/aweigard/GIMME_AR_simulations/tree/master

Then, create data-generation function to sample from this model, using `gimme`.
```{r data-generation}
sim_generate <- function(condition, 
                         fixed_objects = NULL){
  # obtain fixed parameters
  SimDesign::Attach(fixed_objects)
  
  # obtain condition parameters
  n <- condition$sample_size
  t <- condition$ts_length
  
    sim_dat <- try(sim.gimme(
                   p.con = p.con, 
                   nvar = nvar,
                   AR = AR,
                   dens = dens,
                   p.group = p.group,
                   con.b = con.b,
                   lag.b = lag.b,
                   mat = mat, 
                   lvl = lvl,          
                   t = t,              
                   n.ind = n))
  if(is(sim_dat, 'try-error')) browser()
  
  # save dgp
  saveRDS(sim_dat, file = paste0("output/sim_dat_", n, "_", t,
                                   ".RDS"))
  
  # create list of matrices
  l_dat <- lapply(sim_dat, function(x){
    as.matrix(x$series, ncol = nvar)
  })
  
  # 
  
  
  dat <- list(dat = l_dat,  # don't export parameters, or I get error later on
  parameters = list(paths = sim_dat$paths))
  # levels = sim_dat$levels))
}
```




# Fitting functions
We use standard GIMME, and 3 different threshold methods in mvgimme. 
```{r fitting-methods}
sim_analyse_gimme_default <- function(condition, dat, fixed_objects = NULL){
  
  # obtain fixed objects
  Attach(fixed_objects)
  
  # 
  
  gimme_res <- try(multiverse.gimme(data = dat$dat,
                 ar = TRUE, 
                 subgroup = TRUE,
                 groupcutoff = .75,
                 subcutoff   = .75))
  if(is(gimme_res, 'try-error')) browser()
  
  ret <- list(path_counts = gimme_res[[1]]$path_counts)
  ret
}

sim_analyse_gimme_liberal <- function(condition, dat, fixed_objects = NULL){
  
  # obtain fixed objects
  Attach(fixed_objects)
  
  # 
  
  ret <- multiverse.gimme(data = dat$dat,
                 ar = TRUE, 
                 plot = FALSE,
                 subgroup = TRUE,
                 groupcutoff = .75,
                 subcutoff   = .75,
                 rmsea.cuts = .08,
                 srms.cuts = .08,
                 nnfi.cuts = .90,
                 cfi.cuts = .90)
  ret
  
}

sim_analyse_gimme_strict <- function(condition, dat, fixed_objects = NULL){
  
  # obtain fixed objects
  Attach(fixed_objects)
  
  # 
  
  ret <- multiverse.gimme(data = dat$dat,
                 ar = TRUE, 
                 plot = FALSE,
                 subgroup = TRUE,
                 groupcutoff = .75,
                 subcutoff   = .75,
                 rmsea.cuts = .03,
                 srms.cuts = .03,
                 nnfi.cuts = .97,
                 cfi.cuts = .97
                 )
  ret
  
}

sim_analyse_gimme_threshold1 <- function(condition, dat, fixed_objects = NULL){
  
  # obtain fixed objects
  Attach(fixed_objects)
  
  # 
  
  ret <- multiverse.gimme(data = dat$dat,
                 ar = TRUE, 
                 plot = FALSE,
                 subgroup = TRUE,
                 groupcutoff = .75,
                 subcutoff   = .75,
                 n.excellent = 1)
  ret
  
}



```



# Summary function

This is relevant here: http://philchalmers.github.io/SimDesign/html/04-Auxillary_parameter_recovery.html

```{r summary-function}
sim_summarize <- function(condition, results, fixed_objects = NULL){
  
  # # load dgp from csv
  # dgp_filename <- list.files("output/", pattern = condition)
  # dgp <- read.csv(dgp_filename[[1]])
  # 
  # # compute adjacency matrix true dgp
  # true_dgp <- list()
  # for(i in 1:length(dgp)){
  #   true_dgp[[i]] <- list()
  #   true_dgp[[i]]$path_counts <- ifelse(dgp[[i]]$paths != 0, 1, 0)
  # }
  # 
  # 
  # # summarize information of dgp
  # 
  # 
  # # Analyze difference in counts matrix
  # diff_count <- sum(results$path_counts - true_dgp$path_counts)
  
  # Analyze bias across all individual networks
  
  
  # For testing, compute some useless stat
  # n_paths <- try(sum(results$path_counts))
  typeof(results)
  head(results[[1]])
  index <- 1:length(results)
  # n_paths <- try(do.call(c, lapply(index, function(ind, results) sum(results[[ind]]$path_counts))))
  
  # TODO need to come up with a way to analyze the results that does not throw an error
  n_paths <- try(lapply(seq_along(results), function(i){
    sum(results[[i]]$path_counts)
  }))
  
  if(is(n_paths, 'try-error')) browser()
  # Output
  ret <- c(n_paths = n_paths)
  ret <- unlist(ret)
  return(ret)
  
}
```




# Execute Simulation

```{r}
sim_res <- SimDesign::runSimulation(sim_design, 
                                    replications = 2, 
                                    save_results = TRUE,
                                    generate = sim_generate, 
                                    # analyse = list(
                                    #     gimme = sim_analyse_gimme_default, 
                                    #     liberal = sim_analyse_gimme_liberal,
                                    #     strict = sim_analyse_gimme_strict,
                                    #     threshold = sim_analyse_gimme_threshold1), 
                                    analyse = sim_analyse_gimme_default,
                                    summarise = sim_summarize, 
                                    # save = TRUE, 
                                    # save_seeds = TRUE,
                                    packages = c("mvgimme"), 
                                    fixed_objects = sim_pars,
                                    parallel = TRUE)
```



# Evaluation



