---
title: "gimme-cutoff-singleanalysis.Rmd"
author: "Björn Siepe"
date: "`r Sys.Date()`"
output: html_document
---
Goal of this document is to implement SimDesign with a single analysis fn to debug easily. 
---
title: "GIMME Cutoff Simulation"
author: "Björn Siepe"
date: "`r Sys.Date()`"
output: html_document
---

This document contains code for a small simulation on using different fit index cutoffs
as stopping criteria for GIMME. 

# Preparation
```{r packages}
library(tidyverse)
library(mvgimme)    # multiverse gimme
library(SimDesign)  # simulation design
library(here)
library(ggokabeito)
library(ggh4x)
source(here::here("scripts/aux_funs.R"))

```

This document contains code for a small simulation on using different fit index cutoffs
as stopping criteria for GIMME. 

# Preparation
```{r packages}
library(mvgimme)    # multiverse gimme
library(SimDesign)  # simulation design
library(here)
source(here::here("scripts/aux_funs.R"))

```

Reproducibility
```{r reproducibility}
set.seed(35037)
```





# Simulation settings
Create a design with different sample sizes and time series lengths.
Maybe also different sparsity levels? 
```{r sim-settings}
# sample_sizes <- c(50, 100, 200)
# For testing only:
n_ind <- c(30, 80)
# n_ind <- c(31)
ar <- c(.2)
ind_a <- c(.15, .40)
# ind_a <- c(.15)
ind_phi <- c(.05, .25)
replications <- 500

sim_design <- SimDesign::createDesign(n_ind = n_ind,
                                      ar = ar,
                                      ind_a = ind_a,
                                      ind_phi = ind_phi)


# TODO double check if this works with change_phi and change_a
a_1 <- matrix(c(
  0.00, 0.00, 0.00, 0.00, 0.00, 0.00,
  0.00, 0.00, 0.25, 0.40, 0.00, 0.00,
  0.00, 0.00, 0.00, 0.00, 0.00, 0.00,
  0.00, 0.00, 0.00, 0.00, 0.00, 0.00,
  0.00, 0.00, 0.00, 0.00, 0.00, 0.15,
  0.00, 0.00, 0.35, 0.00, 0.00, 0.00
), nrow = 6, byrow = TRUE)

change_a <- matrix(c(
  0, 0,  0.00000000,  0.00000000, 0,  0.00000000,
  0, 0, -0.01010176, -0.06727818, 0,  0.00000000,
  0, 0,  0.00000000,  0.00000000, 0,  0.00000000,
  0, 0,  0.00000000,  0.00000000, 0,  0.00000000,
  0, 0,  0.20420106,  0.00000000, 0, -0.04994893,
  0, 0, -0.35000000,  0.00000000, 0,  0.00000000
), nrow = 6, byrow = TRUE)

phi_1 <- matrix(c(
  ar, 0.00, 0.00, 0.00, 0.00, 0.00,
  0.00, ar, 0.00, 0.00, 0.10, 0.00,
  0.00, 0.00, ar, 0.00, 0.00, 0.20,
  0.00, 0.00, 0.00, ar, 0.00, 0.00,
  0.00, 0.00, 0.00, 0.00, ar, 0.00,
  0.00, 0.00, 0.00, 0.00, 0.00, ar
), nrow = 6, byrow = TRUE)
change_phi <- matrix(c(
  0.0299806, 0.0000000, 0.0000000,  0.00000000,  0.0000000,  0.00000000,
  0.0000000, 0.1384933, 0.0000000,  0.00000000,  0.2270527,  0.00000000,
  0.0000000, 0.0000000, 0.2266066,  0.00000000,  0.0000000, -0.02793758,
  0.0000000, 0.0000000, 0.0000000, -0.06865572,  0.0000000,  0.00000000,
  0.0000000, 0.0000000, 0.0000000,  0.00000000, -0.1298429,  0.00000000,
  0.0000000, 0.0000000, 0.0000000,  0.00000000,  0.0000000,  0.05377093
), nrow = 6, byrow = TRUE)
phi_2 <- phi_1 + change_phi
phi_list <- list(phi_1, phi_2)

psi_mat <- matrix(data = rep(0, 36), nrow = 6, ncol = 6)
diag(psi_mat) <- rep(1, 6)
psi_list <- list(psi_mat, psi_mat)


sim_pars <- list(
  tp = 100,
  phi_list = phi_list,
  a_1 = a_1,
  psi_list = psi_list,
  change_a = change_a
)

```



# Data Generation

Then, create data-generation function to sample from this model, using `gimme`.
```{r data-generation}
sim_generate <- function(condition, 
                         fixed_objects = NULL){
  
  # obtain fixed parameters
  SimDesign::Attach(fixed_objects)
  
  # obtain condition parameters
  n_ind <- condition$n_ind
  # number of individuals in each group (while accounting for odd numbers)
  group_size <- floor(n_ind / 2)

  # Create group indicators
  group_ind <- c(rep(1, group_size), rep(2, n_ind - group_size))
  ar <- condition$ar
  ind_a <- condition$ind_a
  ind_phi <- condition$ind_phi
  
  # Create matrix list depending on AR effect
  diag(a_1) <- rep(ar, 6)
  nvar <- ncol(a_1)
  a_2 <- a_1 + change_a
  a_list <- list(a_1, a_2)
  tries <- 0
  max_tries <- 100
  while (tries < max_tries) {
    tries <- tries + 1
    sim_dat <- try(simulateVARtest(
                                   A = a_list, 
                                   Phi = phi_list,
                                   Psi = psi_list,
                                   subAssign = group_ind,
                                   N = n_ind,
                                   tp = tp,
                                   indA = ind_a,
                                   indPhi = ind_phi))
     if (!inherits(sim_dat, "try-error")) {
        break
    } else {
        if (tries == max_tries) {
            break
        }
    
    }
  }
  
  # save dgp
  saveRDS(sim_dat, file = paste0(here("output/simulation/sim_dat_"), n_ind, "_", tp,
                                   ".RDS"))
  
  # list of data matrices
  l_dat <- lapply(sim_dat$dataList, function(x){
    as.matrix(x, ncol = nvar)
  })
  
  # list of edge weights
  l_paths <- lapply(sim_dat$indList, function(x){
    x$Paths
  })
  
  # overall counts matrix
  l_counts <- lapply(sim_dat$indList, function(x){
    x$Adj
  })
  path_counts <- Reduce('+', l_counts)
  
  
  dat <- list(dat = l_dat, 
              ind_paths = l_paths, 
              path_counts = path_counts, 
              group_ind = group_ind)
  # levels = sim_dat$levels))
  
  return(dat)
}

```




# Fitting functions

```{r}
sim_analyse_all <- function(condition, dat, fixed_objects = NULL) {
  
  # obtain fixed objects
  Attach(fixed_objects)
  
  # save dgp parameters for later
  dgp_ind_paths <- dat$ind_paths
  dgp_path_counts <- dat$path_counts
  dgp_sub_ind <- dat$group_ind
  
  # Initialize an empty list to store results
  results <- list()
  
  # Perform the first analysis and store the result in the list
  gimme_default <- try(multiverse.gimme(data = dat$dat,
                     ar = TRUE, 
                     subgroup = TRUE,
                     groupcutoffs = 0.75,
                     subcutoffs = 0.75))
  
  results$default <- list(
    path_counts = gimme_default[[1]]$path_counts,
    path_est_mats = gimme_default[[1]]$path_est_mats,
    sub_ind = gimme_default[[1]]$fit$sub_membership,
    dgp_path_counts = dgp_path_counts,
    dgp_ind_paths = dgp_ind_paths,
    dgp_sub_ind = dgp_sub_ind
  )
  
  # Perform the second analysis and store the result in the list
  gimme_liberal <- try(multiverse.gimme(data = dat$dat,
                     ar = TRUE, 
                     subgroup = TRUE,
                     groupcutoffs = 0.75,
                     subcutoffs = 0.75,
                     rmsea.cuts = 0.08,
                     srmr.cuts = 0.08,
                     nnfi.cuts = 0.90,
                     cfi.cuts = 0.90))
  
  results$liberal <- list(
    path_counts = gimme_liberal[[1]]$path_counts,
    path_est_mats = gimme_liberal[[1]]$path_est_mats,
    sub_ind = gimme_liberal[[1]]$fit$sub_membership,
    dgp_path_counts = dgp_path_counts,
    dgp_ind_paths = dgp_ind_paths,
    dgp_sub_ind = dgp_sub_ind
  )
  
  # Perform the third analysis and store the result in the list
  gimme_strict <- try(multiverse.gimme(data = dat$dat,
                     ar = TRUE, 
                     subgroup = TRUE,
                     groupcutoffs = 0.75,
                     subcutoffs = 0.75,
                     rmsea.cuts = 0.03,
                     srmr.cuts = 0.03,
                     nnfi.cuts = 0.97,
                     cfi.cuts = 0.97))
  
  results$strict <- list(
    path_counts = gimme_strict[[1]]$path_counts,
    path_est_mats = gimme_strict[[1]]$path_est_mats,
    sub_ind = gimme_strict[[1]]$fit$sub_membership,
    dgp_path_counts = dgp_path_counts,
    dgp_ind_paths = dgp_ind_paths,
    dgp_sub_ind = dgp_sub_ind
  )
  
  # Perform the fourth analysis and store the result in the list
  gimme_threshold1 <- try(multiverse.gimme(data = dat$dat,
                        ar = TRUE, 
                        subgroup = TRUE,
                        groupcutoffs = 0.75,
                        subcutoffs = 0.75,
                        n.excellent = 1))
  
  results$threshold1 <- list(
    path_counts = gimme_threshold1[[1]]$path_counts,
    path_est_mats = gimme_threshold1[[1]]$path_est_mats,
    sub_ind = gimme_threshold1[[1]]$fit$sub_membership,
    dgp_path_counts = dgp_path_counts,
    dgp_ind_paths = dgp_ind_paths,
    dgp_sub_ind = dgp_sub_ind
  )
  
  # Return the list of results
  return(results)
}

```



# Summary function


Helpers:
```{r}
#--- Compute Precision
precision <- function(true, est){

  # true paths relative to all paths
  true_pos <- sum(true & est)
  all_pos <- sum(est)
  
  if(is.na(all_pos)){
    return(NA)
  }
  else if (all_pos == 0) {
    return(0)
  } else {
    precision <- true_pos / all_pos
    return(precision)
  }
}

#--- Compute Recall
recall <- function(true, est) {

  true_pos <- sum(true & est)
  all_true <- sum(true)
  
  if(is.na(all_true)){
    return(NA)
  }
  else if (all_true == 0) {
    return(0)
  } else {
    recall <- true_pos / all_true
    return(recall)
  }
}




#--- Nondirected Adjacency matrix
nondirect_adjacency <- function(adj_mat) {
  # Number of ariables
  n_adj_vars <- nrow(adj_mat)
  
  # Initialize symmetrical matrix with 0s
  sym_matrix <- matrix(0, nrow = n_adj_vars, ncol = n_adj_vars)
  
  # Iterate through each cell of the original matrix
  for (i in 1:n_adj_vars) {
    for (j in 1:n_adj_vars) {
      # If there is any effect (1) in either direction, update the symmetrical matrix
      if (n_adj_vars[i, j] == 1 || n_adj_vars[j, i] == 1) {
        sym_matrix[i, j] <- 1
        sym_matrix[j, i] <- 1
      }
    }
  }

  return(sym_matrix)
}


abs_mean <- function(x){
  mean(abs(x), na.rm = TRUE)
}
abs_med <- function(x){
  stats::median(abs(x), na.rm = TRUE)
}

abs_sum <- function(x){
  sum(abs(x), na.rm = TRUE)
}
```


For testing: do not return list of results?


This is relevant here: http://philchalmers.github.io/SimDesign/html/04-Auxillary_parameter_recovery.html

```{r summary-function}
sim_summarize <- function(condition, results, fixed_objects = NULL){

  # browser()
  ret <- list()
  #---- Loop over different analysis fns -----
  for(m in 1:length(results[[1]])){
    
  
  
  #----- Subgroup ------
  ari_sub <- lapply(seq_along(results), function(i){
    
    if(is.null(results[[i]][[m]]$sub_ind)){
      NULL
    } 
    else{
      perturbR:::arandi(results[[i]][[m]]$dgp_sub_ind, results[[i]][[m]]$sub_ind)
    }
    
  })
  
  
  
  #----- Individual -----
  # Compute adjacency matrix for each individual
  # sorry I know this is ugly, I have no more coffee
  for(i in seq_along(results)){
    results[[i]][[m]]$dgp_ind_counts <- lapply(results[[i]][[m]]$dgp_ind_paths,
                                               function(x){
                                                 ifelse(x != 0, 1, 0)
                                               })
    results[[i]][[m]]$ind_counts <- lapply(results[[i]][[m]]$path_est_mats,
                                               function(x){
                                                 ifelse(x != 0, 1, 0)
                                               })
  }
  
  
  # Compare overall path counts
  diff_path_counts <- lapply(seq_along(results), function(i){
    sum(results[[i]][[m]]$dgp_path_counts - results[[i]][[m]]$path_counts)
  })
  
  # Compute bias
  bias_paths <- lapply(seq_along(results), function(i){
     l_diff <- Map('-', results[[i]][[m]]$dgp_ind_paths, results[[i]][[m]]$path_est_mats)
     lapply(l_diff, function(y){as.matrix(y)})
  })
  
  # Precision
  # precision_directed <- lapply(seq_along(results), function(i){
  #   try(precision(results[[i]][[m]]$dgp_path_counts, results[[i]][[m]]$path_counts))
  # })
  precision_directed <- lapply(seq_along(results), function(i){
    Map("precision" ,results[[i]][[m]]$dgp_ind_counts, results[[i]][[m]]$ind_counts)
  })
    

  # Recall
  # recall_directed <- lapply(seq_along(results), function(i){
  #   try(recall(results[[i]][[m]]$dgp_path_counts, results[[i]][[m]]$path_counts))
  # })
  recall_directed <- lapply(seq_along(results), function(i){
    Map("recall" ,results[[i]][[m]]$dgp_ind_counts, results[[i]][[m]]$ind_counts)
  })
  
  
  #----- Aggregate -----
  diff_path_counts_mean <- mean(unlist(diff_path_counts), na.rm = TRUE)
  diff_path_counts_sd <- sd(unlist(diff_path_counts), na.rm = TRUE)
  
  # Aggregate ARI
  ari_mean <- mean(unlist(ari_sub), na.rm = TRUE)
  if(ari_mean < 0){
    ari_mean = 0
    }
  ari_sd <- sd(unlist(ari_sub), na.rm = TRUE)
  ari_mcse <- sqrt((ari_mean*(1-ari_mean)) / replications)
  
  
  # Recall and Precision
  precision_directed_mean <- mean(unlist(precision_directed), na.rm = TRUE)
  precision_directed_mcse <- sqrt((precision_directed_mean*(1-precision_directed_mean)) / replications)
  recall_directed_mean <- mean(unlist(recall_directed), na.rm = TRUE)
  recall_directed_mcse <- sqrt((recall_directed_mean*(1-recall_directed_mean)) / replications)
  
  
  # Aggregate bias
  mean_bias_ests <- lapply(bias_paths, function(x){
    l_tmp <- list()
    mean_mat <- apply(simplify2array(x), 1:2, mean, na.rm = TRUE)
    l_tmp$mean_nonzero_diff <- mean(abs(mean_mat[mean_mat != 0]), na.rm = TRUE)
    l_tmp$var_nonzero_diff <- var(abs(mean_mat[mean_mat != 0]), na.rm = TRUE)
    l_tmp$mean_diff <- mean(abs(mean_mat), na.rm = TRUE)
    l_tmp$var_diff <- var(abs(mean_mat), na.rm = TRUE)
    return(l_tmp)
  })
  
  # for MCSE formulas, see Morris et al. 2019 SIM
  bias_nonzero_mean <- abs_mean(sapply(mean_bias_ests, function(x) x$mean_nonzero_diff))
  bias_nonzero_mcse <- sqrt(sum(sapply(mean_bias_ests, function(x) x$var_nonzero_diff)) / (replications * (replications - 1)))
  bias_mean <- abs_mean(sapply(mean_bias_ests, function(x) x$mean_diff))
  bias_mcse <- sqrt(sum(sapply(mean_bias_ests, function(x) x$var_diff)) / (replications * (replications - 1)))
  
  
  # Output
  ret_mod <- c(ari_m = ari_mean,
           ari_sd = ari_sd,
           ari_mcse = ari_mcse,
           prec_dir_m = precision_directed_mean,
           prec_dir_mcse = precision_directed_mcse,
           recall_dir_m = recall_directed_mean,
           recall_dir_mcse = recall_directed_mcse,
           diff_paths_m = diff_path_counts_mean,
           bias_nonz_m = bias_nonzero_mean,
           bias_nonz_mcse = bias_nonzero_mcse,
           bias_m = bias_mean,
           bias_mcse = bias_mcse
           )
  ret_mod <- round(ret_mod, digits = 5)
  ret_mod <- unlist(ret_mod)
  ret[[m]] <- ret_mod
  
  
  # TODO maybe switch this on again
  names(ret)[m] <- names(results[[1]])[m]
  # Add model name
  # names(ret[[m]]) <- paste0(names(ret[[m]]), names(results[[1]])[m])
  
  }
  

  ret <- unlist(ret)
  # try to cut names to certain length
  
  
  # ret <- unname(ret)
  return(ret)
}
```




# Execute Simulation

```{r}

# for testing second row which throws errors
# sim_design_test <- sim_design[c(1),]
# sim_design_test$n_ind[1] <- 80
# replications = 2
# rows 1,3,5 work
# 2, 4 does not

sim_res <- SimDesign::runSimulation(sim_design, 
                                    replications = replications, 
                                    save_results = TRUE,
                                    # store_results = TRUE, 
                                    generate = sim_generate, 
                                    analyse = sim_analyse_all,
                                    summarise = sim_summarize,
                                    # save = TRUE, 
                                    save_seeds = TRUE,
                                    packages = c("mvgimme", "here"), 
                                    fixed_objects = sim_pars,
                                    parallel = TRUE)
SimClean()


saveRDS(sim_res, file = here("output/sim_res.RDS"))
```

Had to resummarize due to previous bugs, now fixed
```{r}
# sim_res <- SimDesign::reSummarise(sim_summarize,
#                        dir = here("scripts/SimDesign-results_pc04669"))
sim_res <- readRDS(here("output/sim_res.RDS"))

```



# Analyze results
Prepare data to long format:
```{r}
sim_res_long <- sim_res %>% 
  pivot_longer(cols = contains(c("default", "liberal", "strict", "threshold1")),
               names_to = "name", values_to = "value") %>% 
  select(n_ind, ind_a, ind_phi, name, value) %>% 
  separate_wider_delim(cols = "name", delim = ".",
                       names = c("method", "pm"))

```



Prepare visualizations: 
```{r}
palette_okabe_enh <- ggokabeito::palette_okabe_ito(order = c(5,1,3,4,2,6,7,8,9))

```
First for bias: 
```{r}
fig_sim_bias <- sim_res_long %>% 
  filter(pm == "bias_m" | pm == "bias_mcse") %>%
  separate_wider_delim(cols = pm, delim = "_", names = c("pm", "stat")) %>% 
  pivot_wider(id_cols = c(n_ind, ind_a, ind_phi, method, pm), 
              names_from = stat, values_from = value) %>% 
  mutate(ind_a = paste0("P(Ind. Cont.) = ", ind_a)) %>%
  mutate(ind_phi = paste0("P(Ind. Temp.) = ", ind_phi)) %>%
  mutate(across(c(n_ind, ind_a, ind_phi),
                ~as.factor(.))) %>% 
  ggplot(aes(x = n_ind, y = m, color = method, fill = method))+
  geom_errorbar(aes(ymin = m - 1.96*mcse,
                            ymax = m + 1.96*mcse),
                        width = .8, 
                 position = position_dodge(0.5),
                 show.legend = FALSE)+
  geom_point(position = position_dodge(width = 0.5))+
  ggh4x::facet_nested(ind_phi~ind_a)+
  theme_bs()+
  scale_fill_okabe_ito(order = c(5,1,3,4,2,6,7,8,9))+
  scale_color_okabe_ito(order = c(5,1,3,4,2,6,7,8,9))+
  labs(y = "Bias",
       x = "N")+
  scale_y_continuous(lim = c(-0.05,0.1))
fig_sim_bias

ggsave("fig_sim_bias.pdf", fig_sim_bias, path = here("figures/"),
       width = 9, height = 6)

```

Then for Recall:

```{r}
sim_res_long %>% 
 filter(pm == "recall_dir_m" | pm == "recall_dir_mcse") %>%
  separate_wider_delim(cols = pm, delim = "_dir_", names = c("pm", "stat")) %>% 
  pivot_wider(id_cols = c(n_ind, ind_a, ind_phi, method, pm), 
              names_from = stat, values_from = value) %>% 
  mutate(ind_a = paste0("P(Ind. Cont.) = ", ind_a)) %>%
  mutate(ind_phi = paste0("P(Ind. Temp.) = ", ind_phi)) %>%
  mutate(across(c(n_ind, ind_a, ind_phi),
                ~as.factor(.))) %>% 
  ggplot(aes(x = n_ind, y = m, color = method, fill = method))+
  geom_errorbar(aes(ymin = m - 1.96*mcse,
                            ymax = m + 1.96*mcse),
                        width = .8,
                 position = position_dodge(0.5),
                 show.legend = FALSE)+
  geom_point(position = position_dodge(width = 0.5))+
  ggh4x::facet_nested(ind_phi~ind_a)+
  theme_bs()+
  scale_fill_okabe_ito(order = c(5,1,3,4,2,6,7,8,9))+
  scale_color_okabe_ito(order = c(5,1,3,4,2,6,7,8,9))+
  labs(y = "Recall",
       x = "N")


```



Then for Precision:
```{r}
sim_res_long %>% 
 filter(pm == "prec_dir_m" | pm == "prec_dir_mcse") %>%
  separate_wider_delim(cols = pm, delim = "_dir_", names = c("pm", "stat")) %>% 
  pivot_wider(id_cols = c(n_ind, ind_a, ind_phi, method, pm), 
              names_from = stat, values_from = value) %>% 
  mutate(ind_a = paste0("P(Ind. Cont.) = ", ind_a)) %>%
  mutate(ind_phi = paste0("P(Ind. Temp.) = ", ind_phi)) %>%
  mutate(across(c(n_ind, ind_a, ind_phi),
                ~as.factor(.))) %>% 
  ggplot(aes(x = n_ind, y = m, color = method, fill = method))+
  geom_errorbar(aes(ymin = m - 1.96*mcse,
                            ymax = m + 1.96*mcse),
                        width = .8,
                 position = position_dodge(0.5),
                 show.legend = FALSE)+
  geom_point(position = position_dodge(width = 0.5))+
  ggh4x::facet_nested(ind_phi~ind_a)+
  theme_bs()+
  scale_fill_okabe_ito(order = c(5,1,3,4,2,6,7,8,9))+
  scale_color_okabe_ito(order = c(5,1,3,4,2,6,7,8,9))+
  labs(y = "Precision",
       x = "N")

```


Differences in Paths:
```{r}
sim_res_long %>% 
  filter(pm == "diff_paths_m") %>%
  # separate_wider_delim(cols = pm, delim = "_", names = c("pm", "stat")) %>%
  # pivot_wider(id_cols = c(n_ind, ind_a, ind_phi, method, pm), 
  #             names_from = stat, values_from = value) %>% 
  mutate(ind_a = paste0("P(Ind. Cont.) = ", ind_a)) %>%
  mutate(ind_phi = paste0("P(Ind. Temp.) = ", ind_phi)) %>%
  mutate(across(c(n_ind, ind_a, ind_phi),
                ~as.factor(.))) %>% 
  ggplot(aes(x = n_ind, y = value, color = method, fill = method))+
  # geom_errorbar(aes(ymin = m - 1.96*mcse,
  #                           ymax = m + 1.96*mcse),
  #                       width = .8, 
  #                position = position_dodge(0.5),
  #                show.legend = FALSE)+
  geom_point(position = position_dodge(width = 0.5))+
  ggh4x::facet_nested(ind_phi~ind_a)+
  theme_bs()+
  scale_fill_okabe_ito(order = c(5,1,3,4,2,6,7,8,9))+
  scale_color_okabe_ito(order = c(5,1,3,4,2,6,7,8,9))+
  labs(y = "Path Difference",
       x = "N")
```


ARI:
```{r}
sim_res_long %>% 
  filter(pm == "ari_m" | pm == "ari_mcse") %>%
  # separate_wider_delim(cols = pm, delim = "_", names = c("pm", "stat")) %>%
  # pivot_wider(id_cols = c(n_ind, ind_a, ind_phi, method, pm), 
  #             names_from = stat, values_from = value) %>% 
  mutate(ind_a = paste0("P(Ind. Cont.) = ", ind_a)) %>%
  mutate(ind_phi = paste0("P(Ind. Temp.) = ", ind_phi)) %>%
  mutate(across(c(n_ind, ind_a, ind_phi),
                ~as.factor(.))) %>% 
  ggplot(aes(x = n_ind, y = value, color = method, fill = method))+
  # geom_errorbar(aes(ymin = m - 1.96*mcse,
  #                           ymax = m + 1.96*mcse),
  #                       width = .8, 
  #                position = position_dodge(0.5),
  #                show.legend = FALSE)+
  geom_point(position = position_dodge(width = 0.5))+
  ggh4x::facet_nested(ind_phi~ind_a)+
  theme_bs()+
  scale_fill_okabe_ito(order = c(5,1,3,4,2,6,7,8,9))+
  scale_color_okabe_ito(order = c(5,1,3,4,2,6,7,8,9))+
  labs(y = "ARI",
       x = "N")

```



