---
title: "gimme-multiverse"
author: "Björn Siepe"
date: "`r Sys.Date()`"
output: html_document
---

In this document, we perform multiverse analysis for two datasets.


# Preparation
Load all relevant packages:
```{r packages}
library(mvgimme)       # fork of gimmme package that allows multiverse
library(tidyverse)     # data handling
library(here)          # reproducible folder settings

```


# Load reference fits
We load the reference fits, i.e. results of GIMME as reported in the literature. 

```{r load-ref-fits}
ref_fit_pers <- readRDS(here("data/wright_2019/wright_2019_fit_nondetrend.RDS"))
ref_fit_emot <- readRDS(here("data/kullar_2023/kullar_2023_fit.RDS"))
```



# Fit multiverse

Multiverse parameters:
```{r multiverse-params}

group_cuts <- c(.50, .60, .75, .80)
sub_cuts <- c(.50, .60, .75, .80)
rsmea_cuts <- c(.03, .05, .08)
srmr_cuts <- c(.03, .05, .08)
nnfi_cuts <- c(.90, .95, .97)
cfi_cuts <- c(.90, .95, .97)
n_excels <- c(1, 2, 3)

multiverse_grid <- expand.grid(
  group_cuts = group_cuts,
  sub_cuts = rsmea_cuts,
  srmr_cuts = srmr_cuts,
  nnfi_cuts = nnfi_cuts,
  cfi_cuts = cfi_cuts,
  n_excels = n_excels
)

```




## Personality Dataset
```{r multiverse-personality}


```



## Emotion Dataset

```{r multiverse-personality}

```


# Analyze multiverse

## Personality Dataset





## Emotion Dataset



# Visualize Multiverse

## Personality Dataset

### Manuscript


### Supplement


## Emotion Dataset

### Manuscript


### Supplement