---
title: "gimme-multiverse"
author: "Björn Siepe"
date: "`r Sys.Date()`"
output: html_document
---

In this document, we perform a multiverse analysis for two datasets. 
The first dataset is the personality dataset from Wright et al. (2019). The second dataset is the emotion dataset from Kullar et al. (2023).


# Preparation
Load all relevant packages:
```{r packages}
library(mvgimme)       # fork of gimmme package that allows multiverse
library(tidyverse)     # data handling
library(here)          # reproducible folder settings
library(tictoc)        # timing
library(RColorBrewer)  # color palette
source("scripts/aux_funs.R")
set.seed(35037)
```


# Load reference fits
We load the reference fits, i.e. results of GIMME as reported in the literature. 

```{r load-ref-fits}
ref_fit_pers_og <- readRDS(here("data/wright_2019/wright_2019_fit_nondetrend.RDS"))
ref_fit_emot_og <- readRDS(here("data/kullar_2023/kullar_2023_fit.RDS"))
```



# Fit multiverse

Multiverse parameters:
```{r multiverse-params}

group_cuts <- c(.50, .60, .75, .80)
sub_cuts <- c(.50, .60, .75, .80)
rmsea_cuts <- c(.03, .05, .08)
srmr_cuts <- c(.03, .05, .08)
nnfi_cuts <- c(.90, .95, .97)
cfi_cuts <- c(.90, .95, .97)
n_excels <- c(1, 2, 3)

multiverse_grid <- expand.grid(
  group_cuts = group_cuts,
  sub_cuts = sub_cuts,
  rmsea_cuts = rmsea_cuts,
  srmr_cuts = srmr_cuts,
  nnfi_cuts = nnfi_cuts,
  cfi_cuts = cfi_cuts,
  n_excels = n_excels
)

```




## Personality Dataset
```{r multiverse-personality}
data_list <- readRDS(here("data/wright_2019/data_list.RDS"))
tic()
mv_res_pers <- mvgimme::multiverse.gimme(data = here("data/wright_2019/individual_files"),
                                         sep = ",",
                                         header = TRUE,
                                         subgroup = TRUE,
                                         ar = TRUE,
                          groupcutoffs = group_cuts, 
                          subcutoffs = sub_cuts,
                          rmsea.cuts = rmsea_cuts,
                          srmr.cuts = srmr_cuts,
                          nnfi.cuts = nnfi_cuts,
                          cfi.cuts = cfi_cuts,
                          n.excellent = n_excels,
                          n.cores = 60,
                          prune_output = TRUE,
                          save_output = TRUE)
toc()

# saveRDS(mv_res_pers, file = here("output/mv_personality/mv_res_pers2.RDS"))
mv_res_pers <- readRDS(here("output/mv_personality/mv_res_pers2.RDS"))

```





## Emotion Dataset
```{r multiverse-personality}
# Other specification of subgroup cutoffs
sub_cuts_emot <- c(.51, .60, .75, .80)
mv_res_emot <- mvgimme::multiverse.gimme(data = here("data/kullar_2023/finaloutput"),
                                         header = TRUE,
                                         sep = ",",
                                         subgroup = TRUE,
                                         ar = TRUE,
                          groupcutoffs = group_cuts, 
                          subcutoffs = sub_cuts_emot,
                          rmsea.cuts = rmsea_cuts,
                          srmr.cuts = srmr_cuts,
                          nnfi.cuts = nnfi_cuts,
                          cfi.cuts = cfi_cuts,
                          n.excellent = n_excels,
                          n.cores = 60,
                          prune_output = TRUE,
                          save_output = TRUE, 
                          exogenous = "TimeofDay",
                          save_dir = here("output/mv_emotion"))


# 248908.521 sec
# saveRDS(mv_res_emot, file = here("output/mv_emotion/mv_res_emot_new51.RDS"))
mv_res_emot <- readRDS(here("output/mv_emotion/mv_res_emot_new51.RDS"))


```


# Analyze multiverse

## Personality Dataset
Delete reference fit from multiverse dataset.
```{r}
ref_fit_ind <- multiverse_grid %>% 
  mutate(spec = dplyr::row_number()) %>% 
  filter(group_cuts == .75 &
                        sub_cuts == .50 &
                        rmsea_cuts == .05 &
                        srmr_cuts == .05 &
                        nnfi_cuts == .95 &
                        cfi_cuts == .95 &
                        n_excels == 2) %>% 
  pull(spec)

ref_fit_pers <- mv_res_pers[[ref_fit_ind]]
mv_res_pers <- mv_res_pers[-ref_fit_ind]


tic()
comp_pers <- multiverse.compare(mv_res_pers, ref_fit_pers)
toc() # 1439.33 sec elapsed
# saveRDS(comp_pers, here("output/mv_personality/comp_pers_upd.RDS"))
comp_pers <- readRDS(here("output/mv_personality/comp_pers_upd.RDS"))
```


Save a smaller version of the results for sharing the data. The full results are too large, so we only share data used for the main results in the manuscript. This means that we cannot share some of the individual results (e.g. computation based on individual path matrices). The full data are, of course, available upon request. 
```{r}
comp_pers_small <- comp_pers %>% 
  select(!c(l_adj_i, med_diff_edge_i, med_diff_fit_i, l_diff_ests_i, l_diff_adj_i))
saveRDS(comp_pers_small, here("output/mv_personality/comp_pers_small.RDS"))

```





Sanity checks: compare GIMME results to mvgimme
```{r}
g_50_50 <- gimme::gimme(data = here("data/wright_2019/individual_files"),
                                         sep = ",",
                                         header = TRUE,
                                         subgroup = TRUE,
                                         ar = TRUE,
                          groupcutoff = .50, 
                          subcutoff = .50)

g_50_75 <- gimme::gimme(data = here("data/wright_2019/individual_files"),
                                         sep = ",",
                                         header = TRUE,
                                         subgroup = TRUE,
                                         ar = TRUE,
                          groupcutoff = .50, 
                          subcutoff = .75)

g_80_50 <- gimme::gimme(data = here("data/wright_2019/individual_files"),
                                         sep = ",",
                                         header = TRUE,
                                         subgroup = TRUE,
                                         ar = TRUE,
                          groupcutoff = .80, 
                          subcutoff = .50)


# Comparison
g_50_50$fit$sub_membership
g_50_75$fit$sub_membership
g_80_50$fit$sub_membership

ind_50_50 <- multiverse_grid %>% 
  mutate(spec = dplyr::row_number()) %>% 
  filter(group_cuts == .50 &
                        sub_cuts == .50 &
                        rmsea_cuts == .05 &
                        srmr_cuts == .05 &
                        nnfi_cuts == .95 &
                        cfi_cuts == .95 &
                        n_excels == 2) %>% 
    pull(spec)

ind_50_75 <- multiverse_grid %>% 
  mutate(spec = dplyr::row_number()) %>% 
  filter(group_cuts == .50 &
                        sub_cuts == .75 &
                        rmsea_cuts == .05 &
                        srmr_cuts == .05 &
                        nnfi_cuts == .95 &
                        cfi_cuts == .95 &
                        n_excels == 2) %>% 
    pull(spec)

ind_80_50 <- multiverse_grid %>% 
  mutate(spec = dplyr::row_number()) %>% 
  filter(group_cuts == .80 &
                        sub_cuts == .50 &
                        rmsea_cuts == .05 &
                        srmr_cuts == .05 &
                        nnfi_cuts == .95 &
                        cfi_cuts == .95 &
                        n_excels == 2) %>% 
    pull(spec)


# compare results individually
mv_50_50 <- mv_res_pers[[ind_50_50]]
mv_50_75 <- mv_res_pers[[ind_50_75]]
mv_80_50 <- mv_res_pers[[ind_80_50]]

# compare loglikelihood
mv_50_50$fit$logl - g_50_50$fit$logl
mv_50_75$fit$logl - g_50_75$fit$logl
mv_80_50$fit$logl - g_80_50$fit$logl

# Copmpare path counts
mv_50_50$path_counts - g_50_50$path_counts
mv_50_75$path_counts - g_50_75$path_counts
mv_80_50$path_counts - g_80_50$path_counts


```




### Summary statistics
#### Group-Level
Nonconvergence:
```{r}
summary(sapply(mv_res_pers, function(y){
  sum(unlist(lapply(y$path_est_mats, function(x) is.logical(x))))
}))


```


Number of group-level edges:
```{r}
# subtract the 6 AR paths
n_group_paths <- sapply(comp_pers$adjacency_g, function(x) sum(unlist(x))) - 6
summary(n_group_paths)
prop.table(table(n_group_paths))
```
Which group-level paths were found most often?
```{r}
Reduce('+', comp_pers$adjacency_g)

# Heterogeneity
summary(unlist(comp_pers$heterogeneity_g))

# Heterogeneity of original fit (number of converged individuals)
# divide by all effects
all_effects <- ref_fit_pers_og$path_counts
# set AR effects to zero
diag(all_effects[,1:6]) <- 0  
n_group_effects <- sum(all_effects[all_effects == 94]) 
n_all_effects <- sum(all_effects)
n_group_effects/n_all_effects
```



#### Subgroup-Level
Number and size of subgruops
```{r}
summary(unlist(comp_pers$n_sub_g))
table(unlist(comp_pers$size_sub_s))
```


#### Individual-Level
Difference in adjacency matrix:
```{r}
summary(comp_pers$diff_adj_sum_mean_i)
sd(comp_pers$diff_adj_sum_mean_i)
```



Adjacency matrix differences, summed across all individuals within a specification.
```{r}
# Check if there are individuals for whom there was a greater difference
# Custom function to add matrices element-wise
add_matrices <- function(matrix_list) {
  reduce_matrix <- matrix(0, nrow = nrow(matrix_list[[1]]), ncol = ncol(matrix_list[[1]]))
  for (matrix in matrix_list) {
    reduce_matrix <- reduce_matrix + abs(matrix)
  }
  reduce_matrix
}


# both contemporaneous and temporal
result <- lapply(names(comp_pers$l_diff_adj_i[[1]]), function(matrix_name) {
   add_matrices(lapply(comp_pers$l_diff_adj_i, function(element) element[[matrix_name]]))
 })



# calculate average difference
avg_diff_adj <- sapply(result, function(x) sum(abs(x)))/3887
summary(avg_diff_adj)
sum(avg_diff_adj > 4)

```





Edge weight differences
```{r}
hist(comp_pers$mean_nonzero_diff_edge_i)
mean(comp_pers$mean_nonzero_diff_edge_i, na.rm = TRUE)
sd(comp_pers$mean_nonzero_diff_edge_i, na.rm = TRUE)
mean(comp_pers$mean_diff_edge_i)
sd(comp_pers$mean_diff_edge_i)

# compare against average non-zero edge weight in reference fit
mean(unlist(lapply(ref_fit_pers_og$path_est_mats, function(x){
  mean(abs(x[x != 0]))
})), na.rm = TRUE)

```



Identical centrality estimates
```{r}
summary(comp_pers$sum_temp_central_identical_i)
summary(comp_pers$sum_cont_central_identical_i)

# Again, calculate individual differences
l_temp_ident <- list()
l_cont_ident <- list()
for(i in 1:comp_pers$n_ind[[1]]){
  l_temp_ident[[i]] <- lapply(comp_pers$central_node_identical_i, function(x){
    x[[i]]$temp_identical
  })
  l_cont_ident[[i]] <- lapply(comp_pers$central_node_identical_i, function(x){
    x[[i]]$cont_identical
  })
}

# How often are they identical?
most_cent_ident_temp <- sapply(l_temp_ident, function(x){sum(unlist(x))})
sum(most_cent_ident_temp >= 3887)

most_cent_ident_cont <- sapply(l_cont_ident, function(x){sum(unlist(x))})
sum(most_cent_ident_cont >= 3887)

# identical for both
sum(most_cent_ident_temp >= 3887 & most_cent_ident_cont >= 3887)

# identical less than one third
sum(most_cent_ident_temp <= 3887/3)
sum(most_cent_ident_cont <= 3887/3)


```


Fit indices
```{r}
fit_ind_diff <- do.call(rbind, comp_pers$mean_diff_fit_i)
mean_fit_ind_diff <- colMeans(fit_ind_diff)
summary(fit_ind_diff)
```




## Emotion Dataset
Delete reference fit from multiverse dataset.
```{r}
ref_fit_ind <- multiverse_grid %>% 
  mutate(spec = dplyr::row_number()) %>% 
  filter(group_cuts == .75 &
                        sub_cuts == .51 &
                        rmsea_cuts == .05 &
                        srmr_cuts == .05 &
                        nnfi_cuts == .95 &
                        cfi_cuts == .95 &
                        n_excels == 2) %>% 
  pull(spec)

ref_fit_emot <- mv_res_emot[[ref_fit_ind]]
mv_res_emot <- mv_res_emot[-ref_fit_ind]

# Analyze
tic()
comp_emot <- multiverse.compare(mv_res_emot, ref_fit_emot_og)
toc()  # 1660.2 sec elapsed
beepr::beep(6)
# saveRDS(comp_emot, here("output/mv_emotion/comp_emot_upd.RDS"))
comp_emot <- readRDS(here("output/mv_emotion/comp_emot_upd.RDS"))

```

Save a smaller version of the results for sharing the data. The full results are too large, so we only share data used for the main results in the manuscript. This means that we cannot share some of the individual results (e.g. computation based on individual path matrices). The full data are, of course, available upon request. 
```{r}
comp_emot_small <- comp_emot %>% 
  select(!c(l_adj_i, med_diff_edge_i, med_diff_fit_i, l_diff_ests_i, l_diff_adj_i))
saveRDS(comp_emot_small, here("output/mv_emotion/comp_emot_small.RDS"))

```





Sanity check comparison: 
```{r}
g_75_51_emot <- mvgimme::multiverse.gimme(data = here("data/kullar_2023/finaloutput"),
                                         header = TRUE,
                                         sep = ",",
                                         subgroup = TRUE,
                                         ar = TRUE,
                                         groupcutoffs = .75,
                                         subcutoffs = .51,
                                         rmsea.cuts = .05,
                                         srmr.cuts = .05,
                                         nnfi.cuts = .95,
                                         cfi.cuts = .95,
                                         n.excellent = 2,
                                         prune_output = TRUE,
                                         exogenous = "TimeofDay")
# saveRDS(g_75_51_emot, here("output/mv_emotion/g_75_51_emot.RDS"))

# check subgrouping
g_75_51_emot[[1]]$path_counts - ref_fit_emot_og$path_counts

# This 1 % difference changes a lot
subcheck <- Map('-', ref_fit_emot$path_counts_sub, ref_fit_emot_og$path_counts_sub)
sum(abs(unlist(subcheck)))


```




### Summary statistics
#### Group-Level
Nonconvergence:
```{r}
table(sapply(mv_res_emot, function(y){
  sum(unlist(lapply(y$path_est_mats, function(x) is.logical(x))))
}))


```


Number of group-level edges:
```{r}
# subtract the AR paths
n_group_paths <- sapply(comp_emot$adjacency_g, function(x) sum(unlist(x)))
summary(n_group_paths)
prop.table(table(n_group_paths))
```
Which group-level paths were found most often?
```{r}
Reduce('+', comp_emot$adjacency_g)
```

Heterogeneity of the solution
```{r}
summary(unlist(comp_emot$heterogeneity_g))

# Heterogeneity of original fit (number of converged individuals)
# divide by all effects
all_effects <- ref_fit_emot_og$path_counts
# set AR effects to zero
diag(all_effects[,1:9]) <- 0  
n_group_effects <- sum(all_effects[all_effects == 104]) 
n_all_effects <- sum(all_effects)
n_group_effects/n_all_effects

```



#### Subgroup-Level
Number and size of subgruops
```{r}
table(unlist(lapply(mv_res_emot, function(x){
  length(unique(x$fit$sub_membership))
})))

table(unlist(comp_emot$size_sub_s))

# Check number of distinct solutions
length(unique(lapply(comp_emot$size_sub_s, function(x){
  as.character(x)
})))

# Which are these?
unique(lapply(comp_emot$size_sub_s, function(x){
  as.character(x)
}))

```
subgroup membership



ARI and VI
```{r}
table(comp_emot$vi)
table(comp_emot$ari)

# When is ARI low?
comp_emot %>% 
  filter(ari != 1) %>% 
  count(groupcutoffs, subcutoffs)

```





#### Individual-Level
Adjacency matrix differences
```{r}
summary(comp_emot$diff_adj_sum_mean_i)
sd(comp_emot$diff_adj_sum_mean_i)
```



Edge weight differences
```{r}
hist(comp_emot$mean_nonzero_diff_edge_i)
mean(comp_emot$mean_nonzero_diff_edge_i, na.rm = TRUE)
sd(comp_emot$mean_nonzero_diff_edge_i, na.rm = TRUE)
mean(comp_emot$mean_diff_edge_i)
sd(comp_emot$mean_diff_edge_i)

# compare against average non-zero edge weight in reference fit
mean(unlist(lapply(ref_fit_emot_og$path_est_mats, function(x){
  mean(abs(x[x != 0]))
})), na.rm = TRUE)

```



Identical centrality estimates
```{r}
summary(comp_emot$sum_temp_central_identical_i)
summary(comp_emot$sum_cont_central_identical_i)

# Again, calculate individual differences
l_temp_ident <- list()
l_cont_ident <- list()
for(i in 1:comp_emot$n_ind[[1]]){
  l_temp_ident[[i]] <- lapply(comp_emot$central_node_identical_i, function(x){
    x[[i]]$temp_identical
  })
  l_cont_ident[[i]] <- lapply(comp_emot$central_node_identical_i, function(x){
    x[[i]]$cont_identical
  })
}

# How often are they identical?
most_cent_ident_temp <- sapply(l_temp_ident, function(x){sum(unlist(x))})
sum(most_cent_ident_temp >= 3887)

most_cent_ident_cont <- sapply(l_cont_ident, function(x){sum(unlist(x))})
sum(most_cent_ident_cont >= 3887)

# identical for both
sum(most_cent_ident_temp >= 3887 & most_cent_ident_cont >= 3887)

# identical less than one third
sum(most_cent_ident_temp <= 3887/3)
sum(most_cent_ident_cont <= 3887/3)


```


Fit indices
```{r}
fit_ind_diff <- do.call(rbind, comp_emot$mean_diff_fit_i)
mean_fit_ind_diff <- colMeans(fit_ind_diff)
summary(fit_ind_diff)
```














# Visualize Multiverse
Preparation: 
```{r}
# Color palette
palette_3 <- colorRampPalette(brewer.pal(9, "RdBu"))(3)
palette_4 <- colorRampPalette(brewer.pal(9, "RdBu"))(4)

# Set values explicitly 
palette_full <- c(palette_4[1:2], "lightblue", palette_4[3:4])
names(palette_full) <- c("liberal", "medium-liberal", "medium", "medium-strict", "strict")

# Define the desired levels for each factor
group_levels <- c("liberal", "medium-liberal", "medium-strict", "strict")
sub_levels <- c("liberal", "medium-liberal", "medium-strict", "strict")
rmsea_levels <- c("strict", "medium", "liberal")
srmr_levels <- c("strict", "medium", "liberal")
nnfi_levels <- c("liberal", "medium", "strict")
cfi_levels <- c("liberal", "medium", "strict")
n_excels_levels <- c("liberal", "medium", "strict")


```

## Personality Dataset


### SCA Adjacency
Specification curve plot adjacency matrix
```{r}
plot_out_adj_pers <- plot_outcome(mv_res = comp_pers, var = diff_adj_sum_mean_i,
                                  y_label = "Mean of Adjacency Matrix Differences") +
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))+
  # add reference line
  geom_hline(yintercept = 0, color = "black", lty = 2)
plot_spec_adj_pers <- plot_specification(mv_res = comp_pers, var = diff_adj_sum_mean_i)+
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))

# Combine Plots
spec_plot_adj_pers <- cowplot::plot_grid(plot_out_adj_pers, plot_spec_adj_pers, 
                   nrow = 2, align = "h",
                   rel_heights = c(0.5,1))
ggsave("spec_plot_adj_pers.pdf", spec_plot_adj_pers, path = here("figures/"),
       device = "pdf", height = 16, width = 16)
rm(plot_out_adj_pers)
rm(plot_spec_adj_pers)
rm(spec_plot_adj_pers)

```



### Network Multiverse
Network multiverse plot
```{r}
pdf(here("figures/mv_net_pers.pdf"), width = 8, height = 4)
multiverse.network(comp_pers, cutoff = .05, title.cex = 1, label.cex = 1.2, n_ind = 94,
                   fade = TRUE)
dev.off()

```
Visualize reference fit with percentages

```{r}
ref_pct_mat <- ref_fit_pers_og$path_counts/94
ref_pct_mat[abs(ref_pct_mat) < 0.05] <- 0
ref_temp_mat <- ref_pct_mat[,1:6]
ref_cont_mat <- ref_pct_mat[,7:12]

# percentage labels
pct_labels_temp <- paste0(round(t(ref_temp_mat)*100,1), " %")
pct_labels_cont <- paste0(round(t(ref_cont_mat)*100,1), " %")

# 
pdf("figures/ref_multi_net_pers.pdf")
par(mar=c(1,1,1,1))
layout(matrix(c(1,2,3,5,1,4,3,6),ncol=2),heights=c(.5,3.5,.5,3.5))
plot.new()
text(0.5,0.3,"Reference Network",cex=1.3,font=1)
# Temporal
qgraph::qgraph(
      input = t(ref_temp_mat), 
      layout  = "circle",
      lty = 1,
      node.width = 2.5,
      node.height = 2.5,
      edge.labels  = pct_labels_temp,
      theme = "colorblind",
      negDashed = TRUE,
      parallelEdge = TRUE,
      edge.label.cex = 1.5,
      # arrows       = FALSE,
      labels = colnames(ref_cont_mat),    # so that this does not show "lag" in name
      # title.cex = 2, 
      label.cex    = 1.25,
      title = "Temporal",
      maximum = 1)
plot.new()
text(0.5,0.3,"Multiverse Network",cex=1.2,font=1)
# Contemporaneous
qgraph::qgraph(
      input = t(ref_cont_mat), 
      layout  = "circle",
      lty = 1,
      node.width = 2.5,
      node.height = 2.5,
      edge.labels  = pct_labels_cont,
      theme = "colorblind",
      negDashed = TRUE,
      parallelEdge = TRUE,
      edge.label.cex = 1.5,
      # arrows   = FALSE,
      labels = colnames(ref_cont_mat),
      # title.cex = 2,
      label.cex = 1.25,
      title = "Contemporaneous",
      maximum = 1)

multiverse.network(comp_pers, node.width = 2.5,
      node.height = 2.5,cutoff = .05, title.cex = 1, label.cex = 1.25, n_ind = 94,
                   edge.label.cex = 1.5, fade = TRUE)

dev.off()



```




### SCA Density
Specification curve plot density
```{r}
plot_out_dens_pers <- plot_outcome(mv_res = comp_pers, 
                              var = mean_diff_dens_cont_i,
                              y_label = "Density Difference") +
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))+
    # add reference line
  geom_hline(yintercept = 0, color = "black", lty = 2)
plot_spec_dens_pers <- plot_specification(mv_res = comp_pers, var = mean_diff_dens_cont_i)+
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))

# Combine Plots
spec_plot_dens_pers <- cowplot::plot_grid(plot_out_dens_pers, plot_spec_dens_pers, 
                   nrow = 2, align = "h",
                   rel_heights = c(0.5,1))
ggsave("spec_plot_abs_dens_pers.pdf", spec_plot_dens_pers, path = here("figures/"),
       device = "pdf", height = 16, width = 16)

```

Use percentage deviation from original fit
```{r}
ref_dens_cont <- lapply(ref_fit_pers_og$path_est_mats, function(x){
    if(!is.double(x)){
      NA
    }
    else{
      abs_sum(x[, 6:12])
    }
  })
mean_ref_dens_cont<- mean(unlist(ref_dens_cont), na.rm = TRUE)

# We take the negative of the density difference to 
# clearly show when a multiverse network is denser in the plot 

comp_pers$pct_diff_dens_cont <- (-comp_pers$mean_diff_dens_cont_i / mean_ref_dens_cont)*100

plot_out_dens_pers_pct <- plot_outcome(mv_res = comp_pers, 
                              var = pct_diff_dens_cont,
                              y_label = "% Density Difference") +
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))+
      # add reference line
  geom_hline(yintercept = 0, color = "black", lty = 2)
plot_spec_dens_pers_pct <- plot_specification(mv_res = comp_pers, var = pct_diff_dens_cont)+
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))

# Combine Plots
spec_plot_dens_pers <- cowplot::plot_grid(plot_out_dens_pers_pct, plot_spec_dens_pers_pct, 
                   nrow = 2, align = "h",
                   rel_heights = c(0.5,1))
ggsave("spec_plot_dens_pers_pct.pdf", spec_plot_dens_pers, path = here("figures/"),
       device = "pdf", height = 16, width = 16)

rm(plot_out_dens_pers_pct)
rm(plot_spec_dens_pers_pct)
rm(spec_plot_dens_pers)

```




## Emotion Dataset

### SCA Adjacency
Specification curve plot adjacency matrix
```{r}
# for correct colors
sub_cuts <- c(.51, .60, .75, .80)

plot_out_adj_emot <- plot_outcome(mv_res = comp_emot, var = diff_adj_sum_mean_i,
                                  y_label = "Mean of Adjacency Matrix Differences") +
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))+
          # add reference line
  geom_hline(yintercept = 0, color = "black", lty = 2)
plot_spec_adj_emot <- plot_specification(mv_res = comp_emot, var = diff_adj_sum_mean_i)+
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))

# Combine Plots
spec_plot_adj_emot <- cowplot::plot_grid(plot_out_adj_emot, plot_spec_adj_emot, 
                   nrow = 2, align = "h",
                   rel_heights = c(0.5,1))
ggsave("spec_plot_adj_emot.pdf", spec_plot_adj_emot, path = here("figures/"),
       device = "pdf", height = 16, width = 16)

rm(plot_out_adj_emot)
rm(plot_spec_adj_emot)
rm(spec_plot_adj_emot)
```


### Network Multiverse
Network multiverse plot
```{r}
# add better legend/node labels here
temp_labels <- c("HighCorr\nPositive", "HighCorr\nNegative", "Enthusiastic",
                 "Relaxed", "Sad", "Nervous", "Stressed", "MWoccur",
                 "Emotion\nChronometry")
cont_labels <- c(temp_labels, "TimeofDay")

pdf(here("figures/mv_net_emot.pdf"), width = 8, height = 4)
multiverse.network(comp_emot, cutoff = .05, 
                   title.cex = 1, label.cex = 1.2, 
                   n_ind = 105, endogeneous = TRUE, 
                   temp_labels = temp_labels, cont_labels = cont_labels,
                   fade = TRUE)
dev.off()

```


Visualize reference fit with percentages

```{r}
ref_pct_mat <- ref_fit_emot_og$path_counts/104
ref_pct_mat[abs(ref_pct_mat) < 0.05] <- 0
ref_temp_mat <- ref_pct_mat[,1:9]
ref_cont_mat <- ref_pct_mat[,10:19]

# delete empty timeofday row
ref_temp_mat <- ref_temp_mat[-10,]

# percentage labels
pct_labels_temp <- paste0(round(t(ref_temp_mat)*100,1), " %")
pct_labels_cont <- paste0(round(t(ref_cont_mat)*100,1), " %")

# labels
temp_labels <- c("HighCorr\nPositive", "HighCorr\nNegative", "Enthusiastic",
                 "Relaxed", "Sad", "Nervous", "Stressed", "MWoccur",
                 "Emotion\nChronometry")
cont_labels <- c(temp_labels, "TimeofDay")

pdf("figures/ref_multi_net_emot.pdf")
par(mar=c(1,1,1,1))
layout(matrix(c(1,2,3,5,1,4,3,6),ncol=2),heights=c(.5,3.5,.5,3.5))
plot.new()
text(0.5,0.3,"Reference Network",cex=1.3,font=1)
# Temporal

qgraph::qgraph(
      input = t(ref_temp_mat), 
      layout  = "circle",
      lty = 1,
      node.width = 2.5,
      node.height = 2.5,
      edge.labels  = pct_labels_temp,
      theme = "colorblind",
      negDashed = TRUE,
      parallelEdge = TRUE,
      edge.label.cex = 1.5,
      # arrows       = FALSE,
      labels = temp_labels,    # so that this does not show "lag" in name
      # title.cex = 2, 
      label.cex    = 1.25,
      title = "Temporal",
      maximum = 1)
plot.new()
text(0.5,0.3,"Multiverse Network",cex=1.2,font=1)


# Contemporaneous
# create matrix with zero row for endogenous variable
# ref_cont_mat <- rbind(ref_cont_mat, rep(0, 10))

qgraph::qgraph(
      input = t(ref_cont_mat), 
      layout  = "circle",
      lty = 1,
      node.width = 2.5,
      node.height = 2.5,
      edge.labels  = pct_labels_cont,
      theme = "colorblind",
      negDashed = TRUE,
      parallelEdge = TRUE,
      edge.label.cex = 1.5,
      # arrows   = FALSE,
      labels = cont_labels,
      # title.cex = 2,
      label.cex = 1.25,
      title = "Contemporaneous",
      maximum = 1)



multiverse.network(comp_emot, cutoff = .05, 
                   title.cex = 1, label.cex = 1.25, 
                   n_ind = 105, endogeneous = TRUE, 
                   node.width = 2.5,
                   node.height = 2.5,
                   temp_labels = temp_labels, cont_labels = cont_labels,
                   fade = TRUE)

dev.off()



```


### SCA Density
Specification curve plot density
```{r}
# for correct colors
sub_cuts <- c(.51, .60, .75, .80)


plot_out_dens_emot <- plot_outcome(mv_res = comp_emot, 
                              var = mean_diff_dens_cont_i,
                              y_label = "Density Difference") +
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))
plot_spec_dens_emot <- plot_specification(mv_res = comp_emot, var = mean_diff_dens_cont_i)+
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))

# Combine Plots
spec_plot_dens_emot <- cowplot::plot_grid(plot_out_dens_emot, plot_spec_dens_emot, 
                   nrow = 2, align = "h",
                   rel_heights = c(0.5,1))
ggsave("spec_plot_abs_dens_emot.pdf", spec_plot_dens_emot, path = here("figures/"),
       device = "pdf", height = 16, width = 16)

rm(plot_out_dens_emot)
rm(plot_spec_dens_emot)
rm(spec_plot_dens_emot)
```

Use percentage deviation from original fit
```{r}
# for correct colors
sub_cuts <- c(.51, .60, .75, .80)

ref_dens_cont <- lapply(ref_fit_emot_og$path_est_mats, function(x){
    if(!is.double(x)){
      NA
    }
    else{
      abs_sum(x[, 9:19])
    }
  })
mean_ref_dens_cont<- mean(unlist(ref_dens_cont), na.rm = TRUE)

# We take the negative of the density difference to 
# clearly show when a multiverse network is denser in the plot 
comp_emot$pct_diff_dens_cont <- (-comp_emot$mean_diff_dens_cont_i / mean_ref_dens_cont)*100

plot_out_dens_emot_pct <- plot_outcome(mv_res = comp_emot, 
                              var = pct_diff_dens_cont,
                              y_label = "% Density Difference") +
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))+
        # add reference line
  geom_hline(yintercept = 0, color = "black", lty = 2)
plot_spec_dens_emot_pct <- plot_specification(mv_res = comp_emot, var = pct_diff_dens_cont)+
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.5)))

# Combine Plots
spec_plot_dens_emot <- cowplot::plot_grid(plot_out_dens_emot_pct, plot_spec_dens_emot_pct, 
                   nrow = 2, align = "h",
                   rel_heights = c(0.5,1))
ggsave("spec_plot_dens_emot_pct.pdf", spec_plot_dens_emot, path = here("figures/"),
       device = "pdf", height = 16, width = 16)

rm(plot_out_dens_emot_pct)
rm(plot_spec_dens_emot_pct)
rm(spec_plot_dens_emot)



```



# Session Info
```{r}
# create session info
# save as .txt in the main folder
sink("session_info.txt")
sessionInfo()
sink()


```


